formula1

### 2020-07-20 inst/f1points.Rmd
use figure labelling

Finding the maximum likelihood estimate for the players' strengths is
straightforward.  The `hyper2` package includes a suite of numerical
optimization routines, and because they have access to derivatives,
convergence is rapid.

```{r,label=printapiechart,echo=FALSE}
mH <- maxp(H)
mH
pie(maxp(H)[c(1,6,11,2,7,3,8,4,9,5,10)])
```

@@

```{r,label=likevspoints,cache=TRUE,echo=FALSE}
par(pty='s')        # square plot
ox <- dp
oy <- ordertrans(m,dp)
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="official order",ylab="my order",main='Formula 1, 2017 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray') }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

From the above, we see that the first two drivers (Hamilton, Vettel)
are are respectively first and second according to both ranking
ranking procedures; but R\"{a}ikk\"{o}nen *yes I know it is wrong:
rmarkdown is defective* and Bottas are third and fourth, and fourth
and third, according to points and likelihood respectively.  The
degree of agreement between the two systems might be quantified as
"two", for the positions of the top two drivers agree.

>>>>

Finding the maximum likelihood estimate for the players' strengths is
straightforward.  The `hyper2` package includes a suite of numerical
optimization routines, and because they have access to derivatives,
convergence is rapid.  A graphical illustration of the strengths is
given in figure \ref{piechartstrength}

```{r,label=printapiechart,echo=FALSE,fig.cap="Maximum likelihood estimates \\label{piechartstrength} of the strengths of the top-ranked 11 drivers in the 2017 Formula 1 season"}
mH <- maxp(H)
mH
pie(maxp(H)[c(1,6,11,2,7,3,8,4,9,5,10)])
```

@@

```{r,label=likevspoints,cache=TRUE,echo=FALSE,fig.cap="Ordering of the \\label{orderingbypointsandlikelihood} top-ranked 11 drivers in the 2017 Formula 1 season.  Horizontal axis gives official (points-based) order, and the vertical axis gives the likelihood horder.    Thus the points-based ordering would be Hamilton, Vettel, R\"{a}ikk\"{o}nen YES I KNOW IT IS WRONG: RMARKDOWN IS DEFECTIVE while the likelihood ordering is (reading vertically) Hamilton, Vettel, Bottas"}
par(pty='s')        # square plot
ox <- dp
oy <- ordertrans(m,dp)
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="official order",ylab="my order",main='Formula 1, 2017 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray') }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

From figure \r=ef{orderingbypointsandlikelihood}, we see that the
first two drivers (Hamilton, Vettel) are are respectively first and
second according to both ranking ranking procedures; but
R\"{a}ikk\"{o}nen YES I KNOW IT IS WRONG: RMARKDOWN IS DEFECTIVE and
Bottas are third and fourth, and fourth and third, according to points
and likelihood respectively.  The degree of agreement between the two
systems might be quantified as "two", for the positions of the top two
drivers agree.
